Combined Task and Motion Planner through an Interface Layer

### 2015-04-18 documentation/draft.tex
added test and benchmark figures

\usepackage{fancyhdr} % Required for custom headers
\usepackage{float}
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage{graphicx} % Required to insert images
\usepackage{amssymb}
\usepackage{enumerate}

@@

@@

\subsection{Testing}
We generated a set of small-scale tests to check the correctness of the interface layer. ref{fig-smallTest} Each test had three to four blocks initially placed on one or two surfaces. Some blocks were surrounded by three walls, and others were surrounded by 3 walls. This required the interface layer to find the pose that picked up the block in the correct location. Furthermore, some blocks which needed to be moved in order to achieve the goal were obstructed by other blocks, meaning that the other block had to be moved first.

@@

>>>>

\usepackage{fancyhdr} % Required for custom headers
\usepackage{float}
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage{graphicx} % Required to insert images
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{svg}

@@

\DeclareGraphicsExtensions{.jpg,.png,.svg}

@@

\subsection{Testing}
We generated a set of small-scale tests to check the correctness of the interface layer. ref{fig-smallTest} Each test had three to four blocks initially placed on one or two surfaces. Some blocks were surrounded on 3 sides and others on all sides by walls and blocks. For blocks surrounded on 3 sides, the interface layer had to find the pose that picked up the block in the correct direction. For blocks surrounded on all sides, the interface layer needed to generate actions to move blocks in the way.

\begin{figure}[t]
\centering
\def\svgwidth{0.5\textwidth}
\input{figures/smallEnv.pdf_tex}
\caption{Small Environment Test Example. The goal was for the blue blocks to be on surface I and the red blocks to be on surface S.}
\end{figure}

@@

\begin{figure}[t]
\centering
\def\svgwidth{\textwidth}
\input{figures/benchmarks.pdf_tex}
\caption{Benchmarking Test Examples. The goal was to move the green block to another surface.}
\end{figure}
